Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
introduction references added

In the approach to the 2024 U.S. Presidential election, analyzing voter behavior across states and demographic groups is vital for improving the accuracy of electoral outcome predictions. Recent polling data indicate a close competition among primary candidates, including Donald Trump and Kamala Harris, underscoring the importance of precise forecasting. This study employs a Hierarchical Bayesian Model to analyze polling data from all U.S. states, with particular attention to identifying swing states where minor shifts in voter sentiment could significantly impact the results. By examining trends in voter support across states and demographics, this research aims to enhance the accuracy of election predictions by pinpointing the regions most likely to influence the final electoral outcome.

The study's main objective is to estimate state-level vote shares for each candidate, taking into account variables such as regional differences, pollster-specific biases, and the timing of polls relative to Election Day. Key predictors—including polling percentages, sample sizes, and days remaining until the election—are incorporated into the model, which adjusts for variations by state and pollster. The Hierarchical Bayesian Model was selected for its capability to capture intricate data patterns, enabling accurate vote share estimations that mirror the distribution of polling data across diverse U.S. regions.

@@

This research contributes to the field of election forecasting by integrating aggregated polling data with a robust modeling approach, offering insights for political analysts, campaign strategists, and policymakers. By identifying pivotal swing states and addressing possible polling biases, this study provides stakeholders with tools to anticipate shifts in voter preferences and adapt strategies effectively in a dynamic political landscape.

>>>>

In the approach to the 2024 U.S. Presidential election, analyzing voter behavior across states and demographic groups is vital for improving the accuracy of electoral outcome predictions. Recent polling data indicate a close competition among primary candidates, including Donald Trump and Kamala Harris, underscoring the importance of precise forecasting. This study employs a Hierarchical Bayesian Model to analyze polling data from all U.S. states, with particular attention to identifying swing states where minor shifts in voter sentiment could significantly impact the results (@citeModelElection). By examining trends in voter support across states and demographics, this research aims to enhance the accuracy of election predictions by pinpointing the regions most likely to influence the final electoral outcome.

The study's main objective is to estimate state-level vote shares for each candidate, taking into account variables such as regional differences, pollster-specific biases, and the timing of polls relative to Election Day (@citePolls). Key predictors—including polling percentages, sample sizes, and days remaining until the election—are incorporated into the model, which adjusts for variations by state and pollster. The Hierarchical Bayesian Model was selected for its capability to capture intricate data patterns, enabling accurate vote share estimations that mirror the distribution of polling data across diverse U.S. regions.

@@

This research contributes to the field of election forecasting by integrating aggregated polling data with a robust modeling approach, offering insights for political analysts, campaign strategists, and policymakers. By identifying pivotal swing states and addressing possible polling biases, this study provides stakeholders with tools to anticipate shifts in voter preferences and adapt strategies effectively in a dynamic political landscape (@citeSwing).
